Predicting Audio Features with Last.fm Tags

### 2023-03-17 paper/main.tex
use the springer template

\documentclass[fleqn,10pt]{olplainarticle}

\title{Predicting Audio Features with Last.fm Tags}

\author[1]{Jaime Ramírez Castillo}
\author[1]{M. Julia Flores}
\affil[1]{Departamento de Sistemas Informáticos, Universidad de Castilla - La Mancha, Spain}

@@

\begin{abstract}
In this paper, we discuss a number of experiments to analyze the suitability of music label representations to predict certain audio features, such as danceability, loudness, or acousticness...
\end{abstract}

\flushbottom
\maketitle
\thispagestyle{empty}

\section*{Introduction}

Music information retrieval (MIR) is a field that focuses on the analysis, processing and knowledge discovery of information stored in music pieces \cite{ramirez2020machine}.

@@

\section*{State of the Art}

@@

\section*{Generating a Dataset}

@@

\subsection*{A Single-user Dataset}

@@

\subsection*{Last.fm}

@@

\subsubsection*{Last.fm Tags}
Last.fm uses the term \emph{scrobble} to refer to a single track playback,
in a particular moment. We have queried the Last.fm
API to download the user{'}s scrobble logs, reported from 2007 to 2022.
For each scrobble, we have gathered the following information:

@@

\subsection*{Spotify}

@@

\subsection*{Last.fm Tags Representations for Training}

\subsubsection*{Tabular}
Each tag is a column and each cell contains the popularity value of a tag for a track.
A cell is 0 if a tag is missing for a track.

@@

\subsubsection*{Tabular Tokens}

@@

\subsection*{Training Data By Track}

@@

\section*{Experiments}

@@

\subsection*{Models}

@@

\section*{Conclusions}

@@

\section*{Acknowledgments}

@@

\bibliography{sample}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%                                                                 %%
%% Please do not use \input{...} to include other tex files.       %%
%% Submit your LaTeX manuscript as one .tex document.              %%
%%                                                                 %%
%% All additional figures and files should be attached             %%
%% separately and not embedded in the \TeX\ document itself.       %%
%%                                                                 %%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%\documentclass[referee,sn-basic]{sn-jnl}% referee option is meant for double line spacing

%%=======================================================%%
%% to print line numbers in the margin use lineno option %%
%%=======================================================%%

%%\documentclass[lineno,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%======================================================%%
%% to compile with pdflatex/xelatex use pdflatex option %%
%%======================================================%%

%%\documentclass[pdflatex,sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style

%%\documentclass[sn-basic]{sn-jnl}% Basic Springer Nature Reference Style/Chemistry Reference Style
\documentclass[sn-mathphys]{sn-jnl}% Math and Physical Sciences Reference Style
%%\documentclass[sn-aps]{sn-jnl}% American Physical Society (APS) Reference Style
%%\documentclass[sn-vancouver]{sn-jnl}% Vancouver Reference Style
%%\documentclass[sn-apa]{sn-jnl}% APA Reference Style
%%\documentclass[sn-chicago]{sn-jnl}% Chicago-based Humanities Reference Style
%%\documentclass[sn-standardnature]{sn-jnl}% Standard Nature Portfolio Reference Style
%%\documentclass[default]{sn-jnl}% Default
%%\documentclass[default,iicol]{sn-jnl}% Default with double column layout

%%%% Standard Packages
%%<additional latex packages if required can be included here>
%%%%

%%%%%=============================================================================%%%%
%%%%  Remarks: This template is provided to aid authors with the preparation
%%%%  of original research articles intended for submission to journals published
%%%%  by Springer Nature. The guidance has been prepared in partnership with
%%%%  production teams to conform to Springer Nature technical requirements.
%%%%  Editorial and presentation requirements differ among journal portfolios and
%%%%  research disciplines. You may find sections in this template are irrelevant
%%%%  to your work and are empowered to omit any such section if allowed by the
%%%%  journal you intend to submit to. The submission guidelines and policies
%%%%  of the journal take precedence. A detailed User Manual is available in the
%%%%  template package for technical guidance.
%%%%%=============================================================================%%%%

\jyear{2023}%

%% as per the requirement new theorem styles can be included as shown below
\theoremstyle{thmstyleone}%
\newtheorem{theorem}{Theorem}%  meant for continuous numbers
%%\newtheorem{theorem}{Theorem}[section]% meant for sectionwise numbers
%% optional argument [theorem] produces theorem numbering sequence instead of independent numbers for Proposition
\newtheorem{proposition}[theorem]{Proposition}%
%%\newtheorem{proposition}{Proposition}% to get separate numbers for theorem and proposition etc.

\theoremstyle{thmstyletwo}%
\newtheorem{example}{Example}%
\newtheorem{remark}{Remark}%

\theoremstyle{thmstylethree}%
\newtheorem{definition}{Definition}%

\raggedbottom
%%\unnumbered% uncomment this for unnumbered level heads

% JAIME: this is to hide font size warnings
\usepackage{anyfontsize}

\title[Predicting Audio Features with Last.fm Tags]{Predicting Audio Features with Last.fm Tags}

%%=============================================================%%
%% Prefix	-> \pfx{Dr}
%% GivenName	-> \fnm{Joergen W.}
%% Particle	-> \spfx{van der} -> surname prefix
%% FamilyName	-> \sur{Ploeg}
%% Suffix	-> \sfx{IV}
%% NatureName	-> \tanm{Poet Laureate} -> Title after name
%% Degrees	-> \dgr{MSc, PhD}
%% \author*[1,2]{\pfx{Dr} \fnm{Joergen W.} \spfx{van der} \sur{Ploeg} \sfx{IV} \tanm{Poet Laureate}
%%                 \dgr{MSc, PhD}}\email{iauthor@gmail.com}
%%=============================================================%%

\author*[1]{\fnm{Jaime} \sur{Ramírez Castillo}}\email{Jaime.Ramirez@alu.uclm.es}

\author[1]{\fnm{M. Julia} \sur{Flores}}\email{Julia.Flores@uclm.es}
\equalcont{These authors contributed equally to this work.}

% Departamento de Sistemas Informáticos, Universidad de Castilla - La Mancha, Spai

\affil[1]{\orgdiv{Departamento de Sistemas Informáticos}, \orgname{Universidad de Castilla-La Mancha}, \orgaddress{\street{Campus universitario s/n}, \city{Albacete}, \postcode{02071}, \country{Spain}}}

%%==================================%%
%% sample for unstructured abstract %%
%%==================================%%

\abstract{
    In this paper, we discuss a number of experiments to analyze the
    suitability of music label representations to predict certain audio features,
    such as danceability, loudness, or acousticness...
}

%%================================%%
%% Sample for structured abstract %%
%%================================%%

% \abstract{\textbf{Purpose:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
%
% \textbf{Methods:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
%
% \textbf{Results:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.
%
% \textbf{Conclusion:} The abstract serves both as a general introduction to the topic and as a brief, non-technical summary of the main results and their implications. The abstract must not include subheadings (unless expressly permitted in the journal's Instructions to Authors), equations or citations. As a guide the abstract should not exceed 200 words. Most journals do not set a hard limit however authors are advised to check the author instructions for the journal they are submitting to.}

@@

%%\pacs[JEL Classification]{D8, H51}

%%\pacs[MSC Classification]{35A01, 65L10, 65L12, 65L20, 65L70}

\maketitle

\section{Introduction}\label{sec1}

Music information retrieval (MIR) is a field that focuses on the analysis,
processing and knowledge discovery of latent information in music pieces \cite{ramirez2020machine}.

@@

\section{State of the Art}

@@

\section{Generating a Dataset}

@@

\subsection{A Single-user Dataset}

@@

\subsection{Last.fm}

@@

\subsubsection{Last.fm Tags}
Last.fm uses the term \emph{scrobble} to refer to a single track playback,
in a particular moment. We have queried the Last.fm
API to download the user{'}s scrobble logs, reported from 2007 to 2022.
For each scrobble, we have gathered the following information:

@@

\subsection{Spotify}

@@

\subsection{Last.fm Tags Representations for Training}

\subsubsection{Tabular}
Each tag is a column and each cell contains the popularity value of a tag for a track.
A cell is 0 if a tag is missing for a track.

@@

\subsubsection{Tabular Tokens}

@@

\subsection{Training Data By Track}

@@

\section{Experiments}

@@

\subsection{Models}

@@

\section{Conclusions}

@@

\section{Acknowledgments}

@@

%%===========================================================================================%%
%% If you are submitting to one of the Nature Portfolio journals, using the eJP submission   %%
%% system, please include the references within the manuscript file itself. You may do this  %%
%% by copying the reference list from your .bbl file, paste it into the main manuscript .tex %%
%% file, and delete the associated \verb+\bibliography+ commands.                            %%
%%===========================================================================================%%

\bibliography{sn-bibliography}% common bib file
%% if required, the content of .bbl file can be included here once bbl is generated
%%\input sn-article.bbl

%% Default %%
%%\input sn-sample-bib.tex%
